Sampling requirements to detect ecosystem change

### 2020-01-23 R/manuscript_draft.Rmd
edit the case study figure to visualize behavior with several starting number of sample, and for up to 3rd changepoint

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(gridExtra)
p1 <- ggplot(myoutput, aes(final_n,diff_real)) + 
  geom_point(alpha = .3) +
  facet_wrap(~method_f) + theme_bw() +
  labs(title="a",x="", y="Distance to real changepoint")
p2 <- ggplot(myoutput, aes(rep(0, nrow(myoutput)),diff_real))  +
  facet_wrap(~method_f) + 
  geom_violin() +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=.3) + 
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + theme_bw() +
  labs(title="b",x="", y="Distance to real changepoint")
grid.arrange(p1, p2, nrow = 2)
```

>>>>

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 7.2, fig.height= 9}
library(ggplot2)
library(gridExtra)
p1 <- ggplot(myoutput[myoutput$target_cpt==1,], aes(final_n,diff_real, pch=factor(n2_init))) + 
  geom_hline(aes(yintercept=0), col=adjustcolor("black", alpha.f = .4)) + 
  geom_point(alpha = .3) +
  facet_wrap(~method_f) + theme_bw() +
  labs(title="a. First changepoint",x="", y="Distance to real changepoint") +
  theme(legend.position = c(0.95, 0.6),
        legend.background = element_rect(fill = "#ffffffaa", colour = NA),
        legend.title=element_text(size=7), 
        legend.text=element_text(size=8)) +
  guides(pch=guide_legend(title="Initial number\nof sample"))
p2 <- ggplot(myoutput[myoutput$target_cpt==2,], aes(final_n,diff_real, pch=factor(n2_init))) + 
  geom_hline(aes(yintercept=0), col=adjustcolor("black", alpha.f = .4)) + 
  geom_point(alpha = .3) +
  facet_wrap(~method_f) + theme_bw() +
  labs(title="b. Second changepoint",x="", y="Distance to real changepoint") +
  theme(legend.position = c(0.95, 0.6),
        legend.background = element_rect(fill = "#ffffffaa", colour = NA),
        legend.title=element_text(size=7), 
        legend.text=element_text(size=8)) +
  guides(pch=guide_legend(title="Initial number\nof sample"))
p3 <- ggplot(myoutput[myoutput$target_cpt==3,], aes(final_n,diff_real, pch=factor(n2_init))) + 
  geom_hline(aes(yintercept=0), col=adjustcolor("black", alpha.f = .4)) + 
  geom_point(alpha = .3) +
  facet_wrap(~method_f) + theme_bw() +
  labs(title="c. Third changepoint",x="", y="Distance to real changepoint") +
  theme(legend.position = c(0.95, 0.6),
        legend.background = element_rect(fill = "#ffffffaa", colour = NA),
        legend.title=element_text(size=7), 
        legend.text=element_text(size=8)) +
  guides(pch=guide_legend(title="Initial number\nof sample"))
p3
grid.arrange(p1,p2,p3,nrow=3)
```
